---
title: "hw-strings-data612"
author: "Jared 'Jay' Klein and Olivia Triska"
date: "11/15/2021"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(dplyr)
library(stringr)
```


**1. Use R code to write the content of the string "Alaska" without the quotes.**

```{r}
writeLines("Alaska")
```


**2. Use R code to combine the strings "bo" , "nan" , "za".   Separate each string with a backslash**

```{r}
str_c("bo" , "nan" , "za" , sep = "/")
```

**3. For the string, "Mississippi" use R code that will extract the third character through the 6th character and all characters in between**

```{r}
y <- "Mississippi"
str_sub(y, 3,6)
```

**4. Use R code to convert the string “california” to CALIFORNIA  (all caps no quotes)**

```{r}
writeLines(str_to_upper("california"))
```

**5. Using the common words of stringr :: words,  produce R code that will generate all words that start with a u a v or a q**

```{r}
str_subset(words, "^[u|v|q]")
```


**6. Using the common words of stringr :: words,  produce R code that will generate seven letter words that end in t**

```{r}
str_subset(words, "^......t$")
```

**7. Using the common words of stringr :: words,  produce R code that will generate words that end al or el.**

```{r}
str_subset(words,  "(al)$") -> x
str_subset(words,  "(el)$") -> y
union(x,y) 
```

**8. Use stringr functions in order to capitalize all entries for the variable trans of the mpg data frame.**

```{r}
str_to_upper(mpg$trans)
```

**9.  Use a stringr function(s) to find all words that begin with p and end with t from the stringr:words data bank.  How many of these words are there?**

```{r}
str_subset(words, "^p") -> z
str_subset(z, "t$") 
```

**10.  Use a stringr function to determine how many common words from the stringr::words data bank begin with a v.  Use code,  do not count.**
```{r}
length(str_subset(words, "^v"))
```

