---
title: "hw5-DATA-612"
author: "Jared 'Jay' Klein"
date: "10/12/2021"
output: word_document
---

```{r}
install.packages("Lahman")
library(Lahman)
library(tidyverse)
library(dplyr)
library(ggplot2)
```

1) Use r coding to show that the Batting data from the Lahman package  is not a tibble

```{r}
is_tibble(Batting)
```


2) Batting is a very large data frame. Use r code to determine how many rows and columns  the Batting data frame has.

```{r}
dim(Batting)
```

22 columns with 108789 rows. 

3) Now use r coding to convert the Batting data frame to a tibble

```{r}
batting_tib <- as_tibble(Batting)
is_tibble(batting_tib)
```

4)  Use dplyr coding to determine how many and which players hit more than 30 home runs in 1991. (Select playerID , teamID, yearID, and HR)

```{r}
batting_tib%>%
  select(playerID, teamID, yearID, HR)%>%
  filter(yearID == "1991", HR > 30)
  
```


 5) Use any subsetting r code to determine the mean for Home Runs in 1991
 
```{r}
temp_tib <- batting_tib%>%
  select(playerID, teamID, yearID, HR)%>%
  filter(yearID == "1991")

mean(temp_tib[["HR"]])

```
 

6)  Use dplyr coding to determine how many and which players hit more than 30 home runs in 1990.  (Be sure to select player ID , yearID, and  HR)

```{r}
batting_tib%>%
  select(playerID, teamID, yearID, HR)%>%
  filter(yearID == "1990", HR > 30)
```
 
7)  Use any subsetting r code to determine the mean for Home Runs in 1990

```{r}
temp_tib_1990 <- batting_tib%>%
  select(playerID, teamID, yearID, HR)%>%
  filter(yearID == "1990")

mean(temp_tib_1990[["HR"]])
```


8) Use r code to create side by side boxplots showing greater than 30 home run    counts for players in 1990 and 1991.

```{r}
boxplot_tibble <- Batting%>%
  select(yearID, HR)%>%
  filter(yearID %in% c("1990", "1991"), HR > 30)

ggplot(data = boxplot_tibble) +
  geom_boxplot(mapping = aes(y = HR)) +
  facet_wrap(~yearID)
```


9) Recreate box plot

```{r}
Batting%>%
  select(yearID, teamID, HR)%>%
  filter(yearID %in% c("1990", "1991"), HR > 30)%>%
  ggplot(aes(x = teamID, y = HR)) +
  geom_boxplot()
  
```

10) Create a tribble DF

```{r}
tribble (~Name,  ~Age, ~Department, ~YrsofSrvce, ~EduLevel, ~Salary,                   "Carlos", 30,  "Personnel",               4,          "MS",       71500,                   "Jacob",  26,  "Accounting",            6,            "BS",       70000,                   "Elaine",  31,    "IT",                           4,            "BS",      75000,                    "Alice",  42,   "Sales",                        5,          "BS",       72000,                     "Juan",   31,    "IT",                           7,          "BS",        68000,                     "Ray",    28,  "Accounting",             5,          "MS",       81000,                     "Kate",   25,   "Sales",                       4,          "BS",        74000,                    "Leon",   30,  "Personnel",               11,          "MS",     78000,                   "Robert", 29,  "Accounting",              8,          "MS",      77500)-> EmployeeData

EmployeeData
```


11) Recreate Graph

```{r}
ggplot(data = EmployeeData) +
  geom_bar(mapping = aes(x = Name, y = YrsofSrvce, fill = Name), stat = "identity") +
  geom_text(aes(x = Name, y = YrsofSrvce, label = YrsofSrvce), vjust = 2) +
  ggtitle("Years of Service Bar Graph")
```

