---
title: "Homework 1"
author: "Jared 'Jay' Klein and Olivia Triska"
date: "9/15/2021"
output: word_document
---

```{r}
#install.packages("plotly")

library(ggplot2)
library(tidyverse)
library(plotly)
```

1)Explore the Midwest dataframe

```{r}
midwest
```
  a)How many rows, columns, and variables are in the Midwest data frame
```{r}
nrow(midwest)
ncol(midwest)
glimpse(midwest)
```
  There are 437 rows, 28 columns, and 28 features of the dataset with 3 variable types (integer, double, character)
  
  b) Name three categorical variables in the data frame. 
```{r}
library(dplyr)
midwest %>% select(where(is.character)) %>%
  glimpse()
```
    The above are three categorical variables
    
  c) Give a description for the variable per college
```{r}
help("midwest")
```
  Percent college educated in county/pid within the midwestern united states. It is read into R memory as a double data type. It is also a quantitative variable.
  
2) Write R code to produce a histogram for the variable poptotal
```{r}
hist(midwest$poptotal)
```

```{r}
ggplot(data = midwest) +
  geom_histogram(mapping = aes(x=poptotal), bins = 30)

plotly::ggplotly()
```
3) Write r code to produce a boxplot for the variable area, and then use your box plot to find Q1, Q2, and Q3
```{r}
ggplot(data = midwest) +
  geom_boxplot(mapping = aes(y=area))

plotly::ggplotly()
```


4) Write r code to produce side by side boxplots for the quantitative variable area with respect to the categorical variable state.
```{r}
ggplot(data = midwest) +
  geom_boxplot(mapping = aes(x=area, y=state))

plotly::ggplotly()
```


5) Write r code to produce a scatter plot for the variables popdensity and popwhite. Let popdensity be the independent variable x and popwhite be dependent variable y.
```{r}
ggplot(data = midwest) +
  geom_point(mapping = aes(x = popdensity, y=popwhite))

plotly::ggplotly()
```


6) Write r code that will produce smooth lines plots and scatter plots on the same axis system for popwhite and popdensity with respect to the categorical variable state.
```{r}
ggplot(data = midwest) +
  geom_point(mapping = aes(x=popdensity, y=popwhite)) +
  geom_smooth(mapping = aes(x=popdensity, y=popwhite)) +
  facet_wrap(~state)
```


7) Again,  using the variables popdensity and popwhite, write r code that will produce the same basic scatter plot, but also make the following changes: 
  a) Your scatter plot should have purple data points. 
  b) The label of the dependent variable should be changed to Population  Density and the label of the independent variable should be changed to White Population
  c) Add a linear regression line to your graph. 
  d) Add the following title to your graph; White vs Density Scatter Plot
```{r}
ggplot(data = midwest) +
  geom_point(mapping = aes(x=popdensity, y=popwhite), color="purple") +
  geom_smooth(mapping = aes(x=popdensity, y=popwhite), method = lm) +
  xlab("Population Density") +
  ylab("White Population") +
  ggtitle("White vs. Density Scatter Plot") + 
  facet_wrap(~state)
```
  
  
8) Write R code that will generate the following graph (use the mpg data frame)
```{r}
ggplot(data=mpg) +
  geom_point(mapping = aes(x=displ, y=hwy, color=drv)) +
  geom_smooth(mapping=aes(x=displ,y=hwy)) +
  stat_smooth(mapping = aes(x=displ,y=hwy, color=drv))
plotly::ggplotly()
```
#9   Write R code that will produce the following facet plot using the midwest data frame
```{r}
ggplot(data=midwest) +
  geom_boxplot(mapping = aes(y=popdensity)) +
  facet_wrap(~state)
```
#10   Write R code that will produce the following facet plot using the mpg data frame
```{r}
ggplot(data=mpg) +
  geom_histogram(mapping = aes(x=cty), fill = "green") +
  facet_grid(drv ~ cyl)
  
```

  