---
title: "Homework 1"
author: "Jared 'Jay' Klein and Olivia Triska"
date: "9/15/2021"
output: word_document
always_allow_html: true
---

```{r}
#Below line for installing plotly. Used for interactive graphs to solve ?'s. 
#install.packages("plotly")

library(ggplot2)
library(tidyverse)
```

1)Explore the Midwest dataframe

```{r}
head(midwest)
?midwest
```
  a)How many rows, columns, and variables are in the Midwest data frame
```{r}
nrow(midwest)
ncol(midwest)
dim(midwest)
```
  There are 437 rows, 28 columns, and 28 features of the dataset with 3 variable types (integer, double, character)
  
  b) Name three categorical variables in the data frame. 
```{r}
library(dplyr)
midwest %>% select(where(is.character)) %>%
  glimpse()
```
    
  The above are three categorical variables *(county, state, category)
    
  c) Give a description for the variable per college
  
  The variable percollege is quantitative and pertains to the percent of the sampled population that is    has completed a college education. Percollege is kept as a double by R in memory. 
  
2) Write R code to produce a histogram for the variable poptotal
```{r}
ggplot(data = midwest) +
  geom_histogram(mapping = aes(x=poptotal))
```

3) Write r code to produce a boxplot for the variable area, and then use your box plot to find Q1, Q2, and Q3
```{r}
ggplot(data = midwest) +
  geom_boxplot(mapping = aes(y=area))

plotly::ggplotly()
```

Q1 -> about .02 maybe .025
Q3 -> about .04 maybe less
Median/Q2 -> .03 just about
**Note: I found these without using the "summary()" method since the instructions
wanted me to find these values using the plot. 

4) Write r code to produce side by side boxplots for the quantitative variable area with respect to the categorical variable state.
```{r}
ggplot(data = midwest) +
  geom_boxplot(mapping = aes(x=area, y=state))
```


5) Write r code to produce a scatter plot for the variables popdensity and popwhite. Let popdensity be the independent variable x and popwhite be dependent variable y.
```{r}
ggplot(data = midwest) +
  geom_point(mapping = aes(x = popdensity, y=popwhite))
```


6) Write r code that will produce smooth lines plots and scatter plots on the same axis system for popwhite and popdensity with respect to the categorical variable state.
```{r}
ggplot(data = midwest) +
  geom_point(mapping = aes(x=popdensity, y=popwhite, color=state)) +
  geom_smooth(mapping = aes(x=popdensity, y=popwhite, color=state))
```


7) Again,  using the variables popdensity and popwhite, write r code that will produce the same basic scatter plot, but also make the following changes: 
  a) Your scatter plot should have purple data points. 
  b) The label of the dependent variable should be changed to Population  Density and the label of the independent variable should be changed to White Population
  c) Add a linear regression line to your graph. 
  d) Add the following title to your graph; White vs Density Scatter Plot
```{r}
ggplot(data = midwest) +
  geom_point(mapping = aes(x=popdensity, y=popwhite, color=state), 
             color="purple") +
  geom_smooth(mapping = aes(x=popdensity, y=popwhite), method = lm) +
  stat_smooth(mapping = aes(x=popdensity, y=popwhite, color=state)) +
  xlab("Population Density") +
  ylab("White Population") +
  ggtitle("White vs. Density Scatter Plot")
```
  
  
8) Write R code that will generate the following graph (use the mpg data frame)
```{r}
ggplot(data=mpg) +
  geom_point(mapping = aes(x=displ, y=hwy, color=drv)) +
  geom_smooth(mapping=aes(x=displ,y=hwy)) +
  stat_smooth(mapping = aes(x=displ,y=hwy, color=drv))
```
#9   Write R code that will produce the following facet plot using the midwest data frame
```{r}
ggplot(data=midwest) +
  geom_boxplot(mapping = aes(y=popdensity)) +
  facet_wrap(~state)
```
#10   Write R code that will produce the following facet plot using the mpg data frame
```{r}
ggplot(data=mpg) +
  geom_histogram(mapping = aes(x=cty), fill = "green") +
  facet_grid(drv ~ cyl)
```

  