---
title: "hw11-moreregex-data612"
author: "Jared 'Jay' Klein and Olivia Triska"
date: "11/29/2021"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)      
library(stringr)
```

1) Use a string R function and the stringr :: words data set to find all four letter words that have the letter v in any location.
```{r}
four_letter <- str_subset(words, "^....$")
str_subset(four_letter, "v")
```


2) Use a string R function and the stringr :: words data set to find all words that begin with a vowel and end with a vowel.
```{r}
str_subset(words, "^[aeiou].*[aeiou]$")
```

3) Use and show a string R function and the stringr :: words data set to find all words that end in x using the str_subset string r function and the str_detect string r function.
```{r}
str_subset(words, "x$")
str_detect(words, "x$")
```

4) Use and show a string R function and the stringr :: words data set to find all words that contain the four vowels a, e, i, and o.
```{r}
words_with_a <- str_subset(words, "a+")
words_with_a_i <- str_subset(words_with_a, "i+")
words_with_a_i_e <- str_subset(words_with_a_i, "e+")
str_subset(words_with_a_i_e, "o+")
```

5) Use and show a string R function and the stringr :: words data set to confirm or disprove that the letter q is always followed by the letter u
```{r}
str_subset(words, "qu")
str_subset(words, "q(?!u)")
```

