---
title: "classwork5"
author: "Jared 'Jay' Klein"
date: "10/11/2021"
output: word_document
---

# 1) Use the command dim(midwest) to determine how many rows and columns the data table midwest has.
```{r}
library(tidyverse)

dim(midwest)
midwest
```

There are 437 rows and 28 Columns


# 2) Use and show R code to determine if the data table midwest is a tibble.
```{r}
is_tibble(midwest)
```

# 3) Use and show R code to convert midwest to a data frame if it is a tibble. (If it is not a tibble, skip this problem)
```{r}
as.data.frame(midwest)
```

4)  Use and show R code that will extract (subset) the content of the variable area from the # midwest data table using two methods.

```{r}
midwest[["area"]]
```

```{r}
midwest$area
```


5)  Now use and show R code that will extract the variable area by using piping and using a # dplyr command.

```{r}
midwest%>%
  select(area)
```

How does the output of problem 4 differ from the output of problem 5?
  Dplyr looks to be converting the midwest dataframe from a dataframe object to
  a tibble object instead.
  
6)  Use and show R code that will extract (subset) the content of the variable that has the 5th # position in the data table.

```{r}
midwest[[5]]
```


7)  Create a tibble that has three columns.  Column A has the letter b for each entry, column B has# 10 entries that are consecutive multiples of 3. ( 3, 6, 9...), and the last column , column C # consists of the natural log of each value in column B. Show and use R code that will produce the tibble below.

```{r}
tibble(
  A = "b",
  B = 1:10 *3, 
  C = log(B)
)
```


8)  Assign your tibble from problem 7 to a variable and create a scatter plot for variables B and C.# let B be the explanatory variable and let C be the response variable.

```{r}
custom_df <- tibble(
  A = "b",
  B = 1:10 *3, 
  C = log(B)
)

ggplot(data = custom_df) +
  geom_point(mapping = aes(x = B, y = C ))
```





