---
title: "cw-regexmatches-data612"
author: "Jared 'Jay' Klein"
date: "11/15/2021"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(stringr)
```

1. **Given the following vector of strings;  c( “boxing” , “tennis”,  “football”, “rugby”), create a regular expression that will match the pattern  ball  in all possible strings.  Use R code that features a stringr**

```{r}
v1 <- c("boxing", "tennis", "football", "rugby")
str_view(v1, "ball")
```
2. **Given the following vector of strings;  c( “baseball” , “volleyball”,  “football”), create a regular expression that will match the pattern  of any letter to the immediate right of the letter e  in all possible strings.  Use R code that features a stringr function to confirm your answer.**

```{r}
v2 <- c("baseball" , "volleyball",  "football")

str_view(v2, "e.")
```

3. **Given the following vector of strings;  c( “baseball” , “volleyball”,  “football”), create a regular expression that will match a starting letter of  v  for all possible strings of the vector.  Use R code that features a stringr function to confirm your answer.**

```{r}
str_view(v2, "^v[a-zA-Z0-9]+")
```

4. **What regular expression will be produced from the string   "\"\"\"\\"**

*A string without double quotes. So essentially writeLines*

5. **Describe in words what the regular expression,   ( . . . )\\1 , will match**

*Three letters as a group where the three letters repeat once.*
