---
title: "cw10-data612"
author: "Jared 'Jay' Klein"
date: "11/8/2021"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(stringr)
library(dplyr)
```
1 Use R code to remove the double quotes from the given string.  "American"

```{r}
noquote("American")
```


2  Use R code to determine the length of the following string  "American"

```{r}
str_length("American")
```

3  Use R code to join the following three strings.  "Pre", "si",  "dent".  Your answer should be 
one string 

```{r}
str_c("Pre", "si", "dent", sep = "")
```


4  Use and show R code to select the last three letters of the string  "University"

```{r}
str_sub("University", -3, -1)
```


5  Use and show R code to capitalize all letters of the string  "florida"

```{r}
str_to_upper("florida")
```


6  Use and show R code to produce all words that have exactly 7 letters from the string R :: 
words data set.

```{r}
words = stringr::words

str_subset(words, "^.......$")
```


7  Use and show R code to produce all 7 letter words that start with b from the string R :: 
words data set

```{r}
str_subset(words, "^b......$")
```


8  Use the string_view function to identify and output the string  "Atlanta",  from the 
collection of strings  "Boston", "Baltimore", "Houston", "Atlanta", and "Richmond".

```{r}
library(htmlwidgets)

str_view(c("Boston", "Baltimore", "Houston", "Atlanta", "Richmond"), "^Atlanta$")
```


9  Use and show R code to produce all words that begin with a vowel (a,e,i,o,u) from the  
string R :: words data set

```{r}
str_subset(words, "^[a,e,i,o,u]")
```


