---
title: "Lab-1"
author: "Jared 'Jay' Klein"
date: "8/30/2021"
output: word_document
---
1) Use and show R code to find the square root of 63,504.
```{r}
sqrt(63504)
```
2) Use and show R code to log10(45000) 
```{r}
log10(45000)
```
3) Use and show R code to evaluate ln(23.05) 
```{r}
log(23.05)
```
4) Use and show R code to write all integers from 15 to 1 in decreasing order. 
```{r}
c <- seq(from = 15, to = 1)
for (variable in c) {
  print(variable)
}
```
5) Use and show R code to find the mean of all prime numbers 3 to 17 inclusive. 
```{r}
# install.packages("matlab")
library(matlab)

c <- vector()
for (number in 3:17) {
  if (isprime(number)) {
    c <- append(c, number)
  }
}

print(c)
print(mean(c))
```

6) Use and show R code to round 17.3838 to the nearest hundredth
```{r}
round(17.3838, digits = 3)
```
7) Use and show R code to evaluate the expression 7(53 – 2)2 
```{r}
7*(53-2)*2
```
8) Use R code to write a function that will calculate the volume of a cylinder. The following formula will be helpful, V = πr 2h.  Then use your function to calculate the volume of a cylinder that has a radius of 25 and a height of 10
```{r}
vol_of_cyl <- function(radius, height){
  volume <- pi*(radius^2)*height
  return(volume)
}
```

```{r}
vol_of_cyl(radius = 25, height = 10)
```

