---
title: "hw8-data612"
author: "Jared 'Jay' Klein and Olivia Triska"
date: "10/29/2021"
output: word_document
---

```{r}
ld_data <- untidydata::language_diversity
```

```{r}
library(tidyverse)
library(dplyr)
```


2)  The data set is too long (444 rows) and should be wider in order to become 
more useful and understandable.  Use and show R code to produce a table that is 
wider data table version of the original data table.

```{r}
ld_data%>%
  pivot_wider(names_from = Measurement, values_from = Value)
```


3)  Now use and show R code that will arrange the Continents in alphabetical 
order.  Print the first 40 rows.  A partial table showing rows 35 – 40 are given 
below.

```{r}
ld_data%>%
  pivot_wider(names_from = Measurement, values_from = Value)%>%
  arrange(Continent)%>%
  print(n = 40)
```


4)  Now use and show R code that will only produce Asian countries in the data 
table.  There are 16 Asian countries

```{r}
ld_data%>%
  pivot_wider(names_from = Measurement, values_from = Value)%>%
  arrange(Continent)%>%
  filter(Continent == "Asia")
```


5)  Enter the r code untidydata and then select pre_post
      You should produce the following r data call of   untidydata::pre_post
      Produce the pre_post table that shows all 16 rows.
      
```{r}
pp_data <- untidydata::pre_post
pp_data
```

6)  For the pre_post data table, Use and show R code that will eliminate the 
under scores for the variable spec. 

```{r}
pp_data%>%
  mutate(spec = gsub("_", "", spec)) 
```


7) Use and show R code that imports the excel spread sheet into R.  Assign your imported data 
the variable covid.

```{r}
setwd("/Users/jay-macbook/au-datasci/au-data-612-jk/week7/homework")
covid <- read_csv("Covid19Data.csv")
```


8)  The covid data table is too wide.  Apply and show R tyding code that will 
create a longer data table and then print 25 rows of the new data table. 


```{r}
pivot_longer(covid, cols = `1/22/2020`:`10/15/2020`, names_to = "date", values_to = "Cases")
```


9)  Now use and show R code that changes your table from number 8 and will produce a table 
that only shows data for the countries Vietnam, Thailand, and Singapore.  When printed, the 
first ten rows automatically shows data for Singapore.


```{r}
covid%>%
  pivot_longer(cols =c( "1/22/2020":"10/15/2020"),  names_to = "date", values_to = "Cases")%>%
  filter(`Country/Region` == c("Vietnam", "Thailand","Singapore"))%>%
  print(n=10)
```


10a)

```{r}
covid%>%
  pivot_longer(cols = `1/22/2020`:`10/15/2020`, names_to = "date", values_to = "Cases")%>%
  filter(`Country/Region` == c("Vietnam", "Thailand", "Singapore")) -> se_asia_covid
```

```{r}
se_asia_covid%>%
  filter(Cases == 12693)%>%
  select(`Country/Region`, date, Cases)
```
Singapore had 12,693 cases on 4/25/2020


10b)

```{r}
se_asia_covid%>%
  filter(`Country/Region` == "Thailand")%>%
  arrange(desc(Cases))%>%
  select(`Country/Region`, Cases)
```
The maximum number of cases in Thailand was 3652

10c) 

```{r}
se_asia_covid%>%
  summarise(Cases = sum(Cases))
```


10d) 

```{r}
se_asia_covid%>%
  group_by(`Country/Region`)%>%
  summarise(Cases = sum(Cases))
```

