---
title: "Hw3"
author: "Jared 'Jay' Klein and Olivia Traska"
date: "9/25/2021"
output: word_document
---

```{r}
install.packages("reshape2")
library(reshape2)
library(ggplot2)
View(tips)
?tips
```

1.One of the variables of the tips data frame is size.  Using the command   ?tips,provide a definition for size
  Size refers to the size of the party that was providing the tip. For example, if the size of the party was 3 then waiter was serving 3 people at a table.  
  
  
2) Reproduce the bar graph
```{r}
ggplot(data = tips) +
  geom_bar(mapping = aes(x=size, fill=size, color=size), fill="red") + 
  labs(x="size",
       y="count",
       color="Legend",
       title="Bargraph showing counts for tip size")
```

3) Use and show R code to produce a stacked bar graph that shows regions for the variable size with respect to the categorical variable day.  An image of the stacked bar graph is provided below
```{r}
ggplot(data = tips) +
  geom_bar(mapping = aes(x="", y=size, fill=day), position="stack", stat="identity", width = .5) 
```

4.Now use and show R code to create a pie chart using the same variables in problem 3
```{r}
ggplot(tips, aes(x="", y=size, fill=day)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void()
  
  
  #geom_bar(stat="identity", width=1, color="white") +
  #coord_polar("y", start=0)
```


5.Using the variables of the data frame, create a scatter plot showing a relationship between the total bill and the tip percentage of the total bill.x = the total bill,  y =  tip/total bill  (tip divided by total bill)Use your scatter plot from problem 5 to produce the following plots for 6 ,7, and 8.
```{r}
ggplot(data = tips) +
  geom_point(mapping = aes(x=total_bill, y=tip/total_bill)) 
```



6.Facetthe scatter plot over the variable day using two rows.  On what day do you have the most extreme outlier?
```{r}
ggplot(data = tips) +
  geom_point(mapping = aes(x=total_bill, y=tip/total_bill))+
  facet_wrap(~day, nrow=2)
```
  The most extreme outlier appears to be on Sunday where the total bill is < 10 but the tip percentage of the total bill is > .6. 

7.Facet the scatter plot over the two variables time and size using two rows.   For what size and at what time is the scatter plot most populated?
```{r}
ggplot(data = tips) +
  geom_point(mapping = aes(x=total_bill, y=tip/total_bill))+
  facet_wrap(time~size, nrow=2)
```
For a party of size 2 at dinner time appears to be the most populated plot in the facet scatter plot.


8.Now, go back to problem 7,  provide code that will change the day abbreviations in your facet output . i. e.  Fri -> Friday,  Sat -> Saturday ...
```{r}
new_day_names <- as_labeller(
  c("Fri"="Friday", "Sat"="Saturday", "Sun"="Sunday", "Thur"="Thursday")
)

ggplot(data = tips) +
  geom_point(mapping = aes(x=total_bill, y=tip/total_bill))+
  facet_wrap(~day, labeller=new_day_names)
```

