---
title: "cw8-data612"
author: "Jared 'Jay' Klein"
date: "11/1/2021"
output: word_document
---


```{r}
library(tidyverse)
library(dplyr)
```

1)  Use and show R code to show that the variable name is a key for the data table starwars.
```{r}
starwars %>% 
  count(name) %>% 
  filter(n>1)
```


2)  Use and show R code to show that the collection of variables x, y, and z do not constitute a 
key for the data table diamonds.   Which designations for x, y, and z has the highest count?
```{r}
diamonds %>% 
  count(x, y, z) %>% 
  filter(n>1) %>% 
  arrange(desc(n))
```
x = 4.32, y = 4.35, and z = 2.69 have the highest designation count for the dataset. 

3)  Create tribbles for data frames given below; and then, use and show R code that will 
produce an inner join, a left join, a right join, and a full join  (The tribbles should have only 
two columns;  CustomerId and Product  or CustomerId and State)
```{r}
df1 <- tribble(~CustomerId, ~Product,
               1, "Oven",
               2, "Television",
               3, "Mobile",
               4, "WashingMachine",
               5, "Lightnings",
               6, "Ipad"
               )

df2 <- tribble(~CustomerId, ~State,
               2, "California",
               4, "Newyork",
               6, "Santiago",
               7, "Texas",
               8, "Indiana")
```

```{r}
inner_join(df1, df2, "CustomerId")
```
```{r}
left_join(df1, df2, "CustomerId")

```
```{r}
right_join(df1, df2, "CustomerId")

```

```{r}
full_join(df1, df2, "CustomerId")
```

4) Which of your joins from number 3 show only the observations that tribbles have in 
common?

The Inner join is the only kind of join that shows observations that each of the tribble tables have in common. 
