---
title: "hw8-again-joins-data612"
author: "Jared 'Jay' Klein"
date: "11/1/2021"
output: word_document
---

```{r}
library(tidyverse)
library(nycflights13) 
library(dplyr)
?count
```

1) Examine the data table weather from the nycflights13 package.  Find a 
key for the weather data table. (Hint: the key is a collection of two 
variables). Show and use R code to confirm that your selection is a key.

```{r}
weather <- nycflights13::weather
weather%>%
  count(year, month, day, hour, origin, humid)%>%
  filter(n>1)
```


2)
policies
      PolicyNumber EffectiveDate ExpirationDate
                 1    2012-01-01     2012-12-31
                 2    2012-01-01     2012-06-30
                 3    2012-07-01     2012-12-31
                 4    2012-04-01     2012-12-31
claims
      ClaimNumber PolicyNumber ClaimCost
              123            1       100
              124            1      2400
              125            3       350
              126            4      8000
2a) Use and show R code to create tribbles for the two tables given above.
(Hint: put the dates in double quotes)

```{r}
claims <- tribble(      ~ClaimNumber, ~PolicyNumber, ~ClaimCost,
              123,            1,       100,
              124,           1,      2400,
              125,          3,       350,
              126,         4,      8000)

policies <- tribble(
      ~PolicyNumber, ~EffectiveDate, ~ExpirationDate,
                 1,    "2012-01-01",    "2012-12-31",
                 2,    "2012-01-01",     "2012-06-30",
                 3,    "2012-07-01",     "2012-12-31",
                 4,    "2012-04-01",     "2012-12-31")
```

2b) Use and show R code to confirm that PolicyNumber is a key for both 
tables
```{r}
claims%>%
  count(PolicyNumber)%>%
  filter(n>1)

policies%>%
  count(PolicyNumber)%>%
  filter(n>1)
```


2c) Use and show R code to produce a left join for the two tables
```{r}
policies%>%
  left_join(claims, by = "PolicyNumber")
```

2d) Use and show R code to produce a right join for the two tables
```{r}
policies%>%
  right_join(claims, by = "PolicyNumber")
```

2e) Use and show R code to produce an inner join for the two tables
```{r}
policies%>%
  inner_join(claims, by = "PolicyNumber")
```

2f) Use and show R code to produce a full join for the two tables
```{r}
policies%>%
  full_join(claims, by = "PolicyNumber")
```

2g) What joins show the policy number for which no claim has been filed?

  Left join and full join both show policy number 2 for which no claim number 
  has been filed.
  
3) Study and analyze the variables of the flights data table from the 
nycflights13 data package.  Create two different tables from the flights 
data table.  One table (table1a), showing the top 10 destinations and the 
other table (table1b showing the variables carrier, dest, origin, and 
air_time.  Use and show R code to join the two tables, resulting in the 
table shown below.

```{r}
table1a <- flights%>%
  count(dest, name = "destValue") %>% 
  arrange(desc(destValue)) %>% 
  top_n(n=10)

table1b <- flights %>% 
  select(carrier, dest, origin, air_time)
```

```{r}
full_join(table1a, table1b, by="dest")
```

