---
title: "cw7-data612"
author: "Jared 'Jay' Klein"
date: "10/25/2021"
output: word_document
---

```{r}
setwd("/Users/jay-macbook/au-datasci/au-data-612-jk/week7/classwork/")

library(tidyverse)
library(tidyr)
library(dplyr)
```

1)  Show and use R code to import the Billboard excel file posted on blackboard.  Remember to assign the imported file to a variable.

```{r}
billabing_billabong <- read_csv("Copyofbillboard.csv")
```

2)  The Billboard data table is to wide. There are 76 weeks shown in the data table 
horizontally.  Show and use R code to make the table longer. Print the first 10 rows.  A partial table is shown below:

```{r}
head(billabing_billabong)
```

```{r}
longer_billabing <- pivot_longer(billabing_billabong, cols = starts_with("wk"), names_to = "weeks")

head(longer_billabing, 10)
```

3)  Use R code, specifically a dplyr function and a parsing function to remove the wk from each 
entry of the weeks’ column.  Print the first 25 rows.  A partial table is shown below:

```{r}
longer_billabing%>%
  mutate(weeks = parse_number(weeks))
```

